---
title: "Homework 6"
author: "Shane"
date: '`r format(Sys.time(), "%Y-%m-%d")`'
output: github_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
library(tidyverse)
library(modelr)
library(p8105.datasets)

knitr::opts_chunk$set(
	echo = TRUE,
	warning = FALSE,
	fig.width = 8, 
  fig.height = 6,
  out.width = "90%"
)

theme_set(theme_minimal() + theme(legend.position = "bottom"))

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```



# Problem 1

## import data

```{r}
homicide_df = 
  read_csv("data/homicide-data.csv", na = c("", "NA", "Unknown")) %>% 
  mutate(
    city_state = str_c(city, state, sep = "_"),
    victim_age = as.numeric(victim_age),
    resolution = case_when(
      disposition == "Closed without arrest" ~ "unsolved",
      disposition == "Open/No arrest"        ~ "unsolved",
      disposition == "Closed by arrest"      ~ "solved",
    )
  ) %>% 
  filter(
    city_state != "Tulsa_AL", 
    victim_race %in% c("White", "Black")
  ) %>% 
  select(city_state, resolution, victim_age, victim_race, victim_sex)
```

## start with one city.

```{r}
baltimore_df =
  homicide_df %>% 
  filter(city_state == "Baltimore_MD") %>% 
  mutate(resolution = as_factor(resolution))

glm(resolution ~ victim_age + victim_race + victim_sex, 
    data = baltimore_df,
    family = binomial()) %>% 
  broom::tidy() %>% 
  mutate(
    OR = exp(estimate),
    CI_lower = exp(estimate - 1.96 * std.error),
    CI_upper = exp(estimate + 1.96 * std.error)
  ) %>% 
  select(term, OR, starts_with("CI")) %>% 
  knitr::kable(digits = 3)
```

## try this across cities.

```{r}
models_results_df = 
  homicide_df %>% 
  mutate(resolution = as_factor(resolution)) %>% 
  nest(data = -city_state) %>% 
  mutate(
    models = 
      map(.x = data, ~glm(resolution ~ victim_age + victim_race + victim_sex, data = .x, family = binomial())),
    results = map(models, broom::tidy)
  ) %>% 
  select(city_state, results) %>% 
  unnest(results) %>% 
  mutate(
    OR = exp(estimate),
    CI_lower = exp(estimate - 1.96 * std.error),
    CI_upper = exp(estimate + 1.96 * std.error)
  ) %>% 
  select(city_state, term, OR, starts_with("CI")) 
```

## make plot

```{r}
models_results_df %>% 
  filter(term == "victim_sexMale") %>% 
  mutate(city_state = fct_reorder(city_state, OR)) %>% 
  ggplot(aes(x = city_state, y = OR)) + 
  geom_point() + 
  geom_errorbar(aes(ymin = CI_lower, ymax = CI_upper)) + 
  theme(axis.text.x = element_text(angle = 90, hjust = 1))
```



# Problem 2

## load data and set factors

```{r}
baby_df = 
  read_csv("./data/birthweight.csv") %>% 
  mutate(
    babysex = factor(babysex, labels = c("male", "female")),
    frace = factor(frace, labels = c("White", "Black", "Asian", "Puerto Rican", "Other")),
    malform = factor(malform, labels = c("absent", "present")),
    mrace = factor(mrace, labels = c("White", "Black", "Asian", "Puerto Rican"))
  )
```

## model 1

Reading from the data, and go through online material, I think baby’s sex, gestational age in weeks, mother’s weight gain during pregnancy, and average number of cigarettes smoked per day during pregnancy are factors that effect the baby’s birth weight.

I build my model based on the above assumption. 

```{r}
model_fit_1 = lm(bwt ~ gaweeks + babysex + wtgain + smoken, data = baby_df)

baby_df %>% 
  add_predictions(model_fit_1) %>% 
  add_residuals(model_fit_1) %>% 
  ggplot(aes(x = pred, y = resid)) + 
  geom_point() +
  geom_smooth(se = F,size = 0.5)
```

## model 2 & 3

```{r}
model_fit_2 = lm(bwt ~ blength + gaweeks, data = baby_df)

model_fit_3 = lm(bwt ~ blength + bhead + babysex + bhead * blength + bhead * babysex + blength * babysex + blength * bhead * babysex, data = baby_df)
```

## train and test 

```{r}
cv_df = 
  crossv_mc(baby_df, 100) %>% 
  mutate(
    train = map(train,as_tibble),
    test = map(test,as_tibble)
  )
```

```{r}
rmse_df = 
  cv_df %>% 
  mutate(
    mod_1   = map(train, ~lm(bwt ~ gaweeks + babysex + wtgain + smoken, data = .x)),
    mod_2   = map(train, ~lm(bwt ~ blength + gaweeks, data = .x)),
    mod_3   = map(train, ~lm(bwt ~ blength + bhead + babysex + bhead * blength + bhead * babysex + blength * babysex + blength * bhead * babysex, data = .x)) 
  )%>% 
  mutate(
    rmse_1  = map2_dbl(mod_1, test, ~rmse(model = .x, data = .y)),
    rmse_2  = map2_dbl(mod_2, test, ~rmse(model = .x, data = .y)),
    rmse_3  = map2_dbl(mod_3, test, ~rmse(model = .x, data = .y))
  )

rmse_df %>% 
  select(starts_with("rmse")) %>% 
  pivot_longer(
    everything(),
    names_to = "model", 
    values_to = "rmse",
    names_prefix = "rmse_") %>% 
  mutate(model = fct_inorder(model)) %>% 
  ggplot(aes(x = model, y = rmse, fill = model)) + 
  geom_violin() +
  labs( title = "Models by RMSE") +
  scale_x_discrete(labels = c("Model-1","Model-2","Model-3"))
```

The third model has the lowest RMSE, which means this model fits the best with the data. The third model includes factors and interaction factors. 



# Problem 3

## load data

```{r}
weather_df = 
  rnoaa::meteo_pull_monitors(
    c("USW00094728"),
    var = c("PRCP", "TMIN", "TMAX"), 
    date_min = "2017-01-01",
    date_max = "2017-12-31") %>%
  mutate(
    name = recode(id, USW00094728 = "CentralPark_NY"),
    tmin = tmin / 10,
    tmax = tmax / 10) %>%
  select(name, id, everything())
```

## get the value and plot for r-square

```{r}
rsquare_df = 
  weather_df %>% 
  bootstrap(n = 5000) %>% 
  mutate(
    models = map(strap, ~lm(tmax ~ tmin, data = .x)),
    results = map(models, broom::glance)
  ) %>%
  select(-strap, -models) %>% 
  unnest(results) %>% 
  select(.id, r.squared)

rsquare_df %>% 
  ggplot(aes(x = r.squared)) + 
  geom_density()
```

## get the value and plot for log

```{r}
log_df= 
  weather_df %>% 
  modelr::bootstrap(n = 5000) %>% 
  mutate(
    models = map(strap, ~lm(tmax ~ tmin, data = .x)),
    results = map(models, broom::tidy)
  ) %>%
  select(-strap, -models) %>% 
  unnest(results) %>%
  select(.id, term, estimate) %>% 
  pivot_wider(
    names_from = "term", 
    values_from = "estimate"
  ) %>%
  mutate(
    log = log(`(Intercept)`*tmin)
  ) 

log_df %>%
  ggplot(aes(x = log)) + 
  geom_density()
```

From the density plot, the distribution of R Squared is slight left skewness. And the distribution of log(beta0*beta1) is about normal.

## get the 95% confidence interval for both value

```{r}
left_join(rsquare_df, log_df, by = ".id") %>% 
  select(.id, r.squared, log) %>% 
  pivot_longer(
    -.id,
    names_to = "estimates",
    values_to = "value"
  ) %>% 
  select(-.id) %>% 
  group_by(estimates) %>% 
  summarise(
    p2.5 = quantile(value,0.025),
    p97.5 = quantile(value,0.975)
  ) %>% 
  knitr::kable()
```

The 95% confidence interval for $\hat{r}^{2}$ is (0.894, 0.926).

The 95% confidence interval for $\log \left(\hat{\beta}_{0} * \hat{\beta}_{1}\right)$ is (0.894, 0.926).






